\pkg{hesim}: Health Economic Simulation Modeling and Decision Analysis

### 2020-12-21 manuscript.Rnw
Add formal figures for all plots

%% other packages
\usepackage{algorithm}
\usepackage{multirow}
\usepackage{tikz}
\usetikzlibrary{positioning}
\usepackage{caption} 
\captionsetup[table]{skip=5pt}
\usepackage{amsmath}
\DeclareMathOperator*{\argmax}{arg\,max}

@@

<<ce_plane, fig.height = 4, fig.width = 6>>=
library("scales")
strategy_factor <- function (x) {
  factor(x, levels = 1:3, labels = c("SOC", "New 1", "New 2"))
}

@@

@@

<<ceac_simultaneous>>=
ggplot(cea_ictstm$mce,
       aes(x = k, y = prob, col = strategy_factor(strategy_id))) +
  geom_line() +
  xlab("Willingness to pay") +
  ylab("Probability most cost-effective") +
  scale_x_continuous(breaks = seq(0, max(wtp), length.out = 6),
                     label = scales::dollar) +
  scale_colour_discrete(name = "Strategy") +
  theme(legend.position = "bottom")
@

@@

<<ceac_pw>>=
ggplot(cea_pw_ictstm$ceac,
        aes(x = k, y = prob, col = strategy_factor(strategy_id))) +
  geom_line() +
  xlab("Willingness to pay") +
  ylab("Probability most cost-effective") +
  scale_x_continuous(breaks = seq(0, max(wtp), length.out = 6),
                     label = scales::dollar) +
  theme(legend.position = "bottom") +
  scale_colour_discrete(name = "Strategy")
@

@@

<<ceaf>>=
ggplot(cea_ictstm$mce[best == 1],
       aes(x = k, y = prob, col = strategy_factor(strategy_id))) +
  geom_line() +
  xlab("Willingness to pay") +
  ylab("Probability most cost-effective") +
  scale_x_continuous(breaks = seq(0, max(wtp), length.out = 6),
                     label = scales::dollar) +
  theme(legend.position = "bottom") +
  scale_colour_discrete(name = "Strategy")
@

@@

<<evpi>>=
ggplot(cea_ictstm$evpi, aes(x = k, y = evpi)) +
  geom_line()  +
  xlab("Willingness to pay") +
  ylab("Expected value of perfect information") +
  scale_x_continuous(breaks = seq(0, max(wtp), length.out = 6),
                     label = scales::dollar) +
  scale_y_continuous(label = scales::dollar) +
  theme(legend.position = "bottom")
@

>>>>

%% other packages
\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{algorithm}
\usepackage{multirow}
\usepackage{tikz}
\usetikzlibrary{positioning}
\usepackage{caption} 
\captionsetup[table]{skip=5pt}
\usepackage{amsmath}
\DeclareMathOperator*{\argmax}{arg\,max}

@@

<<ce_plane, fig.height = 4, fig.width = 6, fig.show="hide">>=
library("scales")
strategy_factor <- function (x) {
  factor(x, levels = 1:3, labels = c("SOC", "New 1", "New 2"))
}

@@

\begin{figure}[t!]
\centering
\includegraphics{figure/ce_plane-1.pdf}
\caption{Cost-effectiveness plane} \label{fig:ce-plane}
\end{figure}

@@

<<ceac_simultaneous, fig.height = 4, fig.width = 6, fig.show = "hide">>=
ggplot(cea_ictstm$mce,
       aes(x = k, y = prob, col = strategy_factor(strategy_id))) +
  geom_line() +
  xlab("Willingness to pay") +
  ylab("Probability most cost-effective") +
  scale_x_continuous(breaks = seq(0, max(wtp), length.out = 6),
                     label = scales::dollar) +
  scale_colour_discrete(name = "Strategy") +
  theme(legend.position = "bottom")
@

@@

<<ceac_pw, fig.height = 4, fig.width = 6, fig.show = "hide">>=
ggplot(cea_pw_ictstm$ceac,
        aes(x = k, y = prob, col = strategy_factor(strategy_id))) +
  geom_line() +
  xlab("Willingness to pay") +
  ylab("Probability most cost-effective") +
  scale_x_continuous(breaks = seq(0, max(wtp), length.out = 6),
                     label = scales::dollar) +
  theme(legend.position = "bottom") +
  scale_colour_discrete(name = "Strategy")
@

\begin{figure}[t!]
\centering
\begin{subfigure}[b]{.8\textwidth}
\includegraphics{figure/ceac_simultaneous-1.pdf}
\caption{Simultaneous comparison} \label{fig:ceac-simultaneous}
\end{subfigure}
\begin{subfigure}[b]{.8\textwidth}
\includegraphics{figure/ceac_pw-1.pdf}
\caption{Pairwise comparison} \label{fig:ceac-pw}
\end{subfigure}
\caption{Cost-effectiveness acceptability curves}\label{fig:ceac}
\end{figure}

@@

<<ceaf, fig.height = 4, fig.width = 6, fig.show = "hide">>=
ggplot(cea_ictstm$mce[best == 1],
       aes(x = k, y = prob, col = strategy_factor(strategy_id))) +
  geom_line() +
  xlab("Willingness to pay") +
  ylab("Probability most cost-effective") +
  scale_x_continuous(breaks = seq(0, max(wtp), length.out = 6),
                     label = scales::dollar) +
  theme(legend.position = "bottom") +
  scale_colour_discrete(name = "Strategy")
@

\begin{figure}[t!]
\centering
\includegraphics{figure/ceaf-1.pdf}
\caption{Cost-effectiveness acceptability frontier} \label{fig:ceaf}
\end{figure}

@@

<<evpi, fig.height = 4, fig.width = 6, fig.show = "hide">>=
ggplot(cea_ictstm$evpi, aes(x = k, y = evpi)) +
  geom_line()  +
  xlab("Willingness to pay") +
  ylab("Expected value of perfect information") +
  scale_x_continuous(breaks = seq(0, max(wtp), length.out = 6),
                     label = scales::dollar) +
  scale_y_continuous(label = scales::dollar) +
  theme(legend.position = "bottom")
@

\begin{figure}[t!]
\centering
\includegraphics{figure/evpi-1.pdf}
\caption{Expected value of perfect information} \label{fig:evpi}
\end{figure}
